|

### 2021-03-12 03-Chp-Systematic-Review-Tools.Rmd
Send draft of Chapter 2 to Ciara

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
  bookdown::html_document2: default
documentclass: book
---

@@

Because they R.
```
(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
\minitoc <!-- this will include a mini table of contents-->

@@

* Why searching preprints is important

* Why existing methods are not sufficient

* What the medrxivr tool adds

@@

<!----------------------------------------------------------------------------->
## Introduction

Preprints represent an increasingly important source of scientific information. Defined by the The Committee on Publication Ethics (COPE) as ‘a scholarly manuscript posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process’[@committeeonpublicationethicscope2018], preprints serve several purposes. They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]

@@

Being able to systematically search these preprints for the purpose of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.

At present, the medRxiv website allows only simple search queries as opposed to the often complex Boolean logic that information specialists use to query other major databases. Additionally, previous extraction mechanisms for obtaining the results of searches from medRxiv were to go through each record, one-by-one, downloading individual citations. As the scale of the medRxiv database increases, particularly in light of the massive expansion of the repository as a result of COVID, this already time-consuming and error-prone method is not longer feasible.

This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv preprints. The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed. As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary. The GitHub repository^[Available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.

@@

(ref:medrxivr-sr-cap) __Role of `medrxivr` in a systematic review workflow:__ `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching. Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).

@@

The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform the systematic searches as part of the review in Chapter \@ref(sys-rev-heading) and from an informal survey of colleagues and the evidence synthesis and health librarian community on Twitter. These criteria were as follows:

@@

2. support for bulk export of references returned by the search to a file type that can be imported into a reference manager (e.g., _.bib_  or _.ris_); and

3. automated retrieval of the full-text PDFs of relevant records.

@@

<!----------------------------------------------------------------------------->
### Alternative medRxiv/bioRxiv interfaces

Prior development of this tool, an informal audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted. While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.

The first, a platform called Rxivist [@abdill2019], allows users to search preprints from the using keywords. Similar to `medrxivr`, this tool previously scrapped data straight from the medRxiv and bioRxiv websites but as of November 2020, Rxivist also provided access to Cold Spring Harbor API. However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic. The search interface^[Available at https://rxivist.org/] does not allow for complex search strategies using Boolean operators, and there is no option to batch-export the results of a search.

The second, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues using post-publication peer-review such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature. As such, the platform only returns the most recent `r comma(1000)` records by publication date.

Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records which is required for the full-text screening stage of a systematic review.

@@

Work on this tool began in Summer 2019, which initially existed as a collection of scripts built to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading). Following interest from other researchers in using the _ad-hoc_ web-scraping scripts, the initial version of the `medrxivr` package was released in February 2020. Additional development work took place in 2019/2020, allowing for improved searching and exporting functionality.

Early versions of the tool had a reliance on web-scraping data directly from the medRxiv website. Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992]. In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the medRxiv website was regularly updated.

However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data.[@laprie1992]

Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible papers for the review detailed in Chapter \@ref(sys-rev-heading) required expansion to allow for similar searching of the bioRxiv repository.

<!----------------------------------------------------------------------------->
### Package infrastructure

@@

<!-----------------------------------------------------------------------------> 
## Usage

@@

* An interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
* A collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.

The standard workflow is to download a copy of the metadata, and then run your searchers locally. This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.

@@

Alternatively, the development version of the package can be installed from GitHub:
&nbsp;

@@

<!----------------------------------------------------------------------------->
### Importing preprint metadata

@@

``` {r, eval = FALSE}
# Get a copy of the database from the live medRxiv API endpoint
mx_data <- mx_api_content()  
```

@@

The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am. This method removes the dependency on the API which can become unavailable during peak usage times. The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).

@@

(ref:medrxivr-data-sources-cap) __Overview of `medrxivr` data sources:__ Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function. Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.

@@

The first step is to create your search strategy. Terms to be combined with the OR operator are contained in vectors, while topics to be combined with the AND operator are contained in lists.

@@

For example, the search above written in standard syntax would be: "((dementia __OR__ alzheimer's) __AND__ (lipids __OR__ statins))".

Once a local copy of the database has been created and your search strategy has been defined, both are passed to the `mx_search()` function.

@@

The search also supports common syntax used by systematic reviewers and health librarians, including the use of NEAR statements (which allows for identification of co-localised terms) and wildcards (which allow for alternate spellings, e.g. "randomi*s*ation" vs "randomi*z*ation").

<!----------------------------------------------------------------------------->
### Refining your search

@@

```{r, eval = FALSE}
results  <- mx_search(mx_data,
                      c("dementia", "alzheimer's"),
                      report = TRUE)
```

@@

This allows users to discover which aspects of their search is contributing most to the total results returned. This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.

@@

<!----------------------------------------------------------------------------->
### Exporting to a bibliography file

In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager. While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is

For example, the results of our simple search above can be exported using the following code:

``` {r, eval = FALSE}
mx_export(results, 
          file = "medrxiv_export.bib",
          report = TRUE)
```

@@

<!----------------------------------------------------------------------------->
### Downloading the PDFs of relevant records

Finally, `medrxivr` allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)). `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user. This functionality is similar to the "Find Full Text" feature offered by EndNote.

@@

```{r, eval = FALSE}
mx_download(results,  # Object containing included records
            "pdf/")   # Directory to save PDFs to 
```

@@

<!----------------------------------------------------------------------------->
## Discussion

@@

The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported. It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]

Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online. ^[https://github.com/ropensci/software-review/issues/380] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.

Lobbying of the Cold Springs Harbor Laboratoryto develop the API to allow for direct searching of the database has been ongoing. This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches. For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.

@@

<!----------------------------------------------------------------------------->
### Limitations of `medrxivr`

@@

There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.

@@

<!----------------------------------------------------------------------------->
### Role of open source tools in evidence synthesis

_Not sure where this should go, but keen to include it_

Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b;@mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]

<!----------------------------------------------------------------------------->
## Summary

* In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.

* I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).

* I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers. I have also discussed the tools reception to date, a roadmap for its future development and its place in the broader evidence synthesis in R ecosystem.

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

@@

Because they R.
```

(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}

\minitoc <!-- this will include a mini table of contents-->

@@

-   Why searching preprints is important

-   Why existing methods are not sufficient

-   What the `medrxivr` tool adds

@@

## Introduction

Preprints represent an increasingly important source of scientific information. Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes. They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]

@@

Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature. At the time of writing, however, the bioRxiv.medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations. As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.

This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv and bioRxiv preprints. The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed. As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary of the work done on this project. The GitHub repository[^chp-systematic-review-tools-1] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.

[^chp-systematic-review-tools-1]: Available at <https://github.com/ropensci/medrxivr>

@@

(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching. Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).

@@

The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter. The criteria were as follows:

@@

2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and

3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.

@@

### Alternative medRxiv/bioRxiv interfaces

Prior development of this tool, an audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted. While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.

The first, a platform called Rxivist [@abdill2019], allows users to search preprints using keywords. However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic. The search interface[^chp-systematic-review-tools-2] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.

[^chp-systematic-review-tools-2]: Available at <https://rxivist.org/>

The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature. As such, the platform only returns the most recent `r comma(1000)` records by publication date.

Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.

@@

Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading). Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and the initial version of the `medrxivr` R package was released in February 2020.

Early versions of the tool had a reliance on scraping data directly from the repository website. Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992]. In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the repository website was regularly updated.

However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory. This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]

### Package infrastructure

@@

## Usage

@@

-   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
-   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.

The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy. This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.

While the package allows for users to search both medRxiv and bioRxiv, as the process is identical for both, the examples in the sections are limited to the medRxiv repository.

@@

Alternatively, the development version of the package can be installed from GitHub:

@@

### Importing preprint metadata

@@

```{r, eval = FALSE}
# Get a copy of the database from the live medRxiv API endpoint
mx_data <- mx_api_content()  
```

@@

The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`. Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times. The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).

@@

(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function. Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.

@@

Once a local copy of the metadata is created, the first step in searching it is to create a search strategy. Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(…)`).

@@

For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))". There is now limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for. Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g. "randomi*s*ation" vs "randomi*z*ation".

Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.

@@

### Refining your search

@@

```{r, eval = FALSE}
results  <- mx_search(mx_data,
                      c("dementia", "alzheimer's"), # Combined with OR
                      report = TRUE)
```

@@

This allows users to discover which terms in their search are contributing most to the total number of results returned. This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered. It also aids in identifying misspelled search terms, which will frequently return no results.

@@

### Exporting to a bibliography file

In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager. While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.

For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:

```{r, eval = FALSE}
mx_export(results, 
          file = "medrxiv_export.bib",
          report = TRUE)
```

@@

### Downloading the PDFs of relevant records

`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)). `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user. This functionality is similar to the "Find Full Text" feature offered by EndNote.

@@

```{r, eval = FALSE}
mx_download(results,  # Search results, less excluded records
            "pdf/")   # Directory to save PDFs to 
```

@@

## Discussion

@@

The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported. It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]

[^chp-systematic-review-tools-3]: <https://twitter.com/L_Brierley/status/1233109086444695553>

Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web",[CITE] and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online. [^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.

[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>

[Add bit about the benefits of the rOpenSci review process]

Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing. This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches. For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.

@@

### Limitations of `medrxivr`

@@

There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues. (This disagress with the use cases listed in the intro!)

@@

### Role of open source tools in evidence synthesis

*Not sure where this should go, but keen to include it*

Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]

## Summary

-   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.

-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).

-   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers. I have also discussed the tools reception to date, a roadmap for its future development and its place in the broader evidence synthesis in R ecosystem.
